Economic Evaluation of Geographically Weighted Regression Analysis for Site-specific Nitrogen Management

### 2022-09-07 Writing/manuscript_gwr.rmd
finalized manuscript for PA

```{r cache = F}
#--- packages ---#
library(data.table)
library(tidyverse)
library(flextable)
library(stringr)
library(sf)
library(lfe)
library(modelsummary)
library(patchwork)
```

@@

```{r include = FALSE}
# /*===========================================================
#' # Prepare data and results for writing
# /*===========================================================
#* source all the functions in the Functions folder
fs::dir_ls(here("GitControlled", "Codes", "Functions"), full.names = TRUE) %>%
  lapply(., function(x) source(x))

#* read the results rds file
results <-
  here("Shared", "Results", "pi_data.rds") %>%
  readRDS() %>%
  .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
  .[, bias := pi_diff_est - pi_diff]

pi_dif_gwr <-
  results[, .(pi_dif = mean(pi_diff)), by = type] %>%
  .[, diff(pi_dif)]

#* create figures
source(here("GitControlled", "Codes", "3_make_figures_publication.R"))
```

@@

To find the bias in estimating the value of VRA, the l rofitsof the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR. Estimated per-ha net revenues for SCAM-based URA and GWR-based VRA are found as follows:

@@

Figure \@ref(fig:bias-est-eonr) provides insights into this phenomenon, which shows the distribution of average ratio of estimated EONR to true EONR. A value lower than 1 means EONR is underestimated on average. GWR-R tends to over-estimate EONR at lower price ratios, but the magnitude of over-estimation goes down as the price reatio goes up. The opposite trend is true for GWR-T. At the price ratio of 10.35, the degree of EONR over-estimation is quite significant. Since high-price ratio means nitrogen is relatively expensive, over-estimation of EONR hurts more economically compared to the cases with lower price ratios.

@@

GWR-T exhibits a different pattern of bias. At low price ratios, GWR-T approach has smaller bias compared to GWR-R. This is partially because GWR-T tends to understate the heterogeneity of site-specific yield response function as we saw in figure \@ref(true-vs-estimated-optn-gwr-r). As the price ratio goes up, bias becomes greater. This is due to significant over-estimation of EONR by GWR-T as we saw in figure \@ref(fig:bias-est-eonr). Unlike the GWR-R approach, the distribution of the bias by the GWR-T approach has a fat tail, indicating that there is a greater chance of encountering large positive bias in the value of VRA over URA.

>>>>

```{r cache = F}
#--- packages ---#
library(data.table)
library(tidyverse)
library(flextable)
library(stringr)
library(sf)
library(lfe)
library(modelsummary)
library(patchwork)
library(ggplot2)
```

@@

```{r include = FALSE}
#| include: false

# /*===========================================================
#' # Prepare data and results for writing
# /*===========================================================
#* source all the functions in the Functions folder
fs::dir_ls(here("GitControlled", "Codes", "Functions"), full.names = TRUE) %>%
  lapply(., function(x) source(x))

#* read the results rds file
results <-
  here("Shared", "Results", "pi_data.rds") %>%
  readRDS() %>%
  .[, type := ifelse(transfer == 0, "GWR-R", "GWR-T")] %>%
  .[, bias := pi_diff_est - pi_diff] %>%
  # only display the 25% (5.44), 50% (6.56), 75% (7.67) price ratio
  .[pRatio %in% c(5.44, 6.56, 7.67), ] %>%
  # === label price ratio
  .[, pLabelName := "Price Ratio (N/corn)"] %>%
  .[pRatio == 5.44, pLabel := "Low"] %>%
  .[pRatio == 6.56, pLabel := "Middle"] %>%
  .[pRatio == 7.67, pLabel := "High"] %>%
  .[, pLabel := factor(pLabel, levels = c("Low", "Middle", "High"))]

#* create figures
source(here("GitControlled/Codes/3_make_figures_publication.R"))
```

@@

To find the bias in estimating the value of VRA, the estimated profits of the SCAM-based URA and GWR-based VRA were calculated by plugging in the estimated optimal nitrogen rates into the cell-specific yield response functions estimated by GWR. Estimated per-ha net revenues for SCAM-based URA and GWR-based VRA are found as follows:

@@

Figure \@ref(fig:bias-est-eonr) provides insights into this phenomenon, which shows the distribution of average ratio of estimated EONR to true EONR. A value lower than 1 means EONR is underestimated on average. GWR-R tends to over-estimate EONR at lower price ratios, but the magnitude of over-estimation goes down as the price ratio goes up. The opposite trend is true for GWR-T. At the price ratio of 10.35, the degree of EONR over-estimation is quite significant. Since high-price ratio means nitrogen is relatively expensive, over-estimation of EONR hurts more economically compared to the cases with lower price ratios.

@@

GWR-T exhibits a different pattern of bias. At low price ratios, GWR-T approach has smaller bias compared to GWR-R. This is partially because GWR-T tends to understate the heterogeneity of site-specific yield response function as we saw in figure \@ref(true-vs-estimated-optn-gwr-r). As the price ratio goes up, bias becomes greater. This is due to the significant over-estimation of EONR by GWR-T as we saw in figure \@ref(fig:bias-est-eonr). Unlike the GWR-R approach, the distribution of the bias by the GWR-T approach has a fat tail, indicating that there is a greater chance of encountering large positive bias in the value of VRA over URA.
